---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BOE

<!-- badges: start -->

[![R build status](https://github.com/rOpenSpain/BOE/workflows/R-CMD-check/badge.svg)](https://github.com/rOpenSpain/BOE/actions) [![Travis build status](https://travis-ci.org/rOpenSpain/BOE.svg?branch=master)](https://travis-ci.org/rOpenSpain/BOE) [![Codecov test coverage](https://codecov.io/gh/rOpenSpain/BOE/branch/master/graph/badge.svg)](https://codecov.io/gh/rOpenSpain/BOE?branch=master) [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)

<!-- badges: end -->

The goal of BOE is to provide tools to retrieve data from [BOE](https://boe.es) either from the **Boletín Oficial del Estado** or from the BORME **Boletín Oficial del Registro Mercantil del Estado**.

You can see examples of what is capable on the vignette and with more data this [website](https://llrs.github.io/BOE_historico/).

## Installation

You can install it from github with:

``` r
remotes::install_github("rOpenSpain/BOE")
```

## Examples

This is a basic example which shows you how to solve find the identifiers of some elements. The most important data is the sumario (summary) which can be retrieved by the date:

```{r example}
library("BOE")
today <- Sys.Date()
sumario_hoy <- retrieve_sumario(today)
head(sumario_hoy)
```

If we are interested on a publication we can obtain the url of the publication with:

```{r exampleC}
# Say we are interested on the first result:
pdfs <- url_publications(sumario_hoy[1, ])
pdfs # And we can download it with download.file(pdfs)
```

We can open the publication from R with:

```{r browse, echo = TRUE, eval = FALSE}
open_publications(pdfs)
```

If we need to know the BOE code of a publication we can do so with:

```{r codes}
sumario_xml(as.Date("2019/11/15"))
sumario_xml(as.Date("2019/11/15"), journal = "BORME")
# The codes of publication is the year and the number of said publication
sumario_nbo("2017", "275") 
sumario_nbo("2017", "275", journal = "BORME") 
anuncio("2012", "32498") 
disposicion("2012", "32498")
```

## Code of Conduct

Please note that the BOE project is released with a [Contributor Code of Conduct](https://contributor-covenat.org/version/1/0/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
