---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BOE

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/llrs/BOE.svg?branch=master)](https://travis-ci.org/llrs/BOE)
[![Codecov test coverage](https://codecov.io/gh/llrs/BOE/branch/master/graph/badge.svg)](https://codecov.io/gh/llrs/BOE?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of BOE is to provide tools to retrieve data from BOE

## Installation

You can install the released version of BOE from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("BOE")
```

Or you can install it from github with:

``` r
devtools::install_github("llrs/BOE")
```

## Example

This is a basic example which shows you how to solve find the identifiers of some elements.
The most important data is the sumario (summary) which can be retrieved by the date:

```{r example}
library("BOE")
today <- Sys.Date()
sumario_code <- sumario_xml(today) #Code needed to identify it online
sumario_hoy <- tidy_sumario(get_xml(query_xml(sumario_code)))
head(sumario_hoy)

# Say we are interested on the first result:
year <- format(today, "%Y")
month <- format(today, "%m")
day <- format(today, "%d")
publication_code <- sumario_hoy[1, "publication"]
pdf <- query_pdf(year, month, day, publication_code)
pdf
# And we can download it with download.file(pdf)
```

You can also build the publication code with:
```{r}
sumario_xml(as.Date("2019/11/15"))
# The codes of publication is the year and the number of said publication
sumario_nbo("2017", "275") 
anuncio("2012", "32498") 
disposicion("2012", "32498")
```

