---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(BOE)
```

# Introduction

The goal of BOE is to provide tools to retrieve data from BOE.
The main point of this program is to access the summaries each day [BOE](https://boe.es) provides.
It provides functions to tidy the *sumario* and retrieve the individual ".pdf" of each publication and summaries.

# Sumario

It is a summary of the publications of the day with information about the 
summary number, section, departament, epigraph, brief text of the publication, 
publication's number of pages of the pdf.

The easiest way to get a *sumario* is using [`retrieve_sumario()`]:

```{r sumario}
today <- Sys.Date()
sumario_hoy <- retrieve_sumario(today)
head(sumario_hoy)
```

# Publications

Once you select those publications

```{r}
url_publications(sumario_hoy[1:5, ])
```

# Session Info {-}

```{r session_info}
sessionInfo()
```

