---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(BOE)
```

# Introduction

The goal of BOE is to provide tools to retrieve data from [BOE](https://boe.es) the official gazette of Spain.
Since 2009 the online documents have all the legal validation, but documents published before are accessible from the website too.

The main point of this program is to access the summaries each day [BOE](https://boe.es) provides.
It provides functions to tidy the *sumario* and retrieve the individual ".pdf" of each publication and summaries. 
To retrieve a document we need the publication code.
For summaries we can use two types of codes BOE-S-YYYYMMDD useful to retrieve a document of certain date or BOE-S-YYYY-NNN if we know in which summary was it published. 
To check if a code is valid there is the [`check_code()`] function.

At the same site we can access the [BORME](https://boe.es/diario_borme/) which is another journal to register of organizations commercial activity. 
The summaries from this journal can also be retrieved using the option `journal = "BORME"`. 


# Sumario

It is a summary of the publications of the day with information about the 
summary number, section, departament, epigraph, brief text of the publication, 
publication's number of pages of the pdf.

The easiest way to get a *sumario* is using [`retrieve_sumario()`]:

```{r sumario}
today <- Sys.Date()
sumario_hoy <- retrieve_sumario(today)
head(sumario_hoy)
```

# Publications

Once you select those publications

```{r}
url_publications(sumario_hoy[1:5, ])
```

# Session Info {-}

```{r session_info}
sessionInfo()
```

